Individual and Differential Harm in Redistricting

### 2022-03-29 paper/paper.Rmd
ex figures

To illustrate the concepts and measures we introduce, we will make use of three running examples, which are stylized representations of U.S. states: Mininois, Minissouri, and Minichussets.
Mininois has one large Democratic city which can electorally dominate the rest of the state; Minissouri has two medium-sized cities which are not large enough to deliver a statewide Democratic majority; and Minichusetts has a uniform 3--2 Democratic split in every precinct.
Each example state has the same population and should be divided into 3 districts with population between 54 and 66.
Voters' preferences are assumed to be stable across elections, and turnout is 100%.
Schematics for these examples are shown in Figure \ref{fig:mini-schematic}(a)--(c).

@@

@@

```{r mini-harm, fig.cap="Three potential districting plans for Mininois and Minissouris, showing district partisan lean (top row) and total voter harm versus the counterfactuals in Figure 2(a)-(b) (bottom row; darker shading indicates more harm)."}
include_graphics(here("paper/figures/mini_harm.pdf"))
```

>>>>

To illustrate the concepts and measures we introduce, we will make use of three examples, which are stylized representations of U.S. states: Mininois, Minissouri, and Minichussets.
Mininois has one large Democratic city which can electorally dominate the rest of the state; Minissouri has two medium-sized cities which are not large enough to deliver a statewide Democratic majority; and Minichusetts has a uniform 3--2 Democratic split in every precinct.
Each example state has the same population and should be divided into 3 districts with population between 54 and 66.
Voters' preferences are assumed to be stable across elections, and turnout is 100%.
Schematics for these examples are shown in Figure \ref{fig:mini-schematic}(a)--(c).

@@

```{r harm-mininois, fig.cap="Two potential districting plans for Mininois: a Democratic gerrymander (a) and a close-to-proportional plan (b). Panel (c) shows the total harm to voters in each precinct done by (a), using (b) as a counterfactual."}
include_graphics(here("paper/figures/harm_mininois.pdf"))
```

@@

```{r diffharm-minissouri, fig.cap="Three potential districting plans for Minissouris: a Democratic gerrymander (a), a close-to-proportional plan (b), and a Republican gerrymander (c). Panels (d) and (f) show the total harm to voters in each precinct done by their corresponding gerrymander, using (b) as a counterfactual.  Panel (e) summarizes this harm by party and across precincts, showing the average harm done to voters of each party by each gerrymander."}
include_graphics(here("paper/figures/diffharm_minissouri.pdf"))
```
